---
title: "Lab 01 - Hello R"
author: "Julie Garrison"
date: "Dec 11 2024"
output: 
  html_document: 
    theme: journal
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

## Exercises

### Exercise 1

datasaurus_dozen has 1846 rows and 3 variables:

The three variables included are: dataset, x and y

dataset: indicates which dataset the data are from
x: x-values
y: y-values

  
### Exercise 2

Let's plot the data in the dino dataset:


```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3


Plot y vs. x for the star dataset

```{r plot-star, fig.height=3, fig.width=6}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

For "dino" 
r=−0.0645
For "star" 
r=−0.0630
These r-values are pretty similar to each other and both are almost zero. This implies that the linear relationships in both datasets are weak since both of values are close to zero

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```

### Exercise 4
Plot y vs. x for the circle dataset


```{r plot-circle, fig.height=3, fig.width=6}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

For "dino" 
r=−0.0645
For "circle" 
r=−0.0683
These r-values are pretty similar to each other and both are almost zero. This implies that the linear relationships in both datasets are weak since both of values are close to zero

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```

### Exercise 5

Plot y vs. x for all


```{r plot-all}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset)) +
  geom_point() +
  facet_wrap(~dataset, ncol = 3) +
  theme(legend.position = "none")
```

```{r cor-all}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```

